Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
garibation...

We provide a new, open-source, cross-platform, highly parallel framework in which researchers may be able to create hypotheses and test them computationally through minimal effort. The framework is well-documented for public release at this time (http://sdm-framework.readthedocs.io), it has already served as the backbone of Chada's Ph.D. thesis. The single-line command ``pip install sdm'' will install the framework on posix-like systems, and single-line commands will let users test the framework, generate some of the figures from Kanerva's theoretical predictions in their own machines, and --- if interested enough ---, test their own theories and improve the framework, and the benchmarks used to evaluate the framework, in open-source fashion. It is our belief that such work is a necessary component towards accelerating research in this promising field.

@@

All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. We invite the reader to take a look and explore a little bit.

The overarching intention here is to not only provide a starting point, but to provide a Framework in which SDM research can be conducted.  Consider, for example, having the ability to compare the results of a new (‘forked’) model to the previous `best' (under a particular benchmark set).  For example, some of the benchmarks that we plan to develop in future research is: how fast is convergence through iterative reading?  How large is the attractor of the critical distance?  How well does the system filter noise?  How well does the system work under the supervised learning task?  And other authors may be able to improve this benchmark set themselves, as is usual in open source development.  It is perhaps this facility of ease to build on top of previous work that seems most exciting at this stage.

Consider the misunderstanding concerning the SDM read operation:  Dr Stan Franklin describes Kanerva's read operation in a way that each hard location, at each dimension, provides only a single bit of information to the read operation (instead of Kanerva's full counter).  We have referred to this modified read operation as Chada read (the tale is that my friend \text{\&} colleague, Dr. Daniel de Magalhães Chada, along with Linhares, did not consult Kanerva's book and only discovered the discrepancy in code and ideas a couple of years afterwards).  Having an open, testable, codebase reduces the possibilities of such misunderstandings in the long run.  Indeed, a high-quality codebase seems to have become a scientific community's form of unequivocally standing behind a consensus. For example, the journal Nature analysed the top-100 cited papers in history, to find:

>>>>

We provide a new, open-source, cross-platform, highly parallel framework in which researchers may be able to create hypotheses and test them computationally through minimal effort. The framework is well-documented for public release at this time (http://sdm-framework.readthedocs.io), it has already served as the backbone of Chada's Ph.D. thesis \citep{chada2016you}. The single-line command ``pip install sdm'' will install the framework on posix-like systems, and single-line commands will let users test the framework, generate some of the figures from Kanerva's theoretical predictions in their own machines, and --- if interested enough ---, test their own theories and improve the framework, and the benchmarks used to evaluate the framework, in open-source fashion. It is our belief that such work is a necessary component towards accelerating research in this promising field.

@@

Beyond speed, I have also strived for \emph{ease of use}.  All the simulations and graphics generated in this thesis are promptly available to be re-executed and explored by those interested. I have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. We invite the reader to take a look and explore a little bit.

The overarching intention here is to not only provide a starting point, but to provide a documented Framework in which SDM research can be conducted.  Consider having the ability to compare the results of a new (‘forked’) model to the previous `best' (under a particular benchmark set).  For example, some of the benchmarks that we plan to develop in future research is: how fast is convergence through iterative reading?  How large is the attractor of the critical distance?  How well does the system filter noise?  How well does the system work under the supervised learning task?  And other authors may be able to improve this benchmark set themselves, as is usual in open source development.  It is perhaps this facility of ease to build on top of previous work that seems most exciting at this stage.

Consider the misunderstanding concerning the SDM read operation:  Dr Stan Franklin describes Kanerva's read operation in a way that each hard location, at each dimension, provides only a single bit of information to the read operation (instead of Kanerva's full counter).  We have referred to this modified read operation as Chada read\footnote{Legend has it that my friend \text{\&} colleague, Dr. Daniel de Magalhães Chada, along with Linhares, did not consult and re-check with Kanerva's book and only discovered the discrepancy in code and ideas a couple of years afterwards.}.  Having an open, testable, codebase reduces the possibilities of such misunderstandings in the long run.  Indeed, a high-quality codebase seems to have become a scientific community's form of unequivocally standing behind a consensus. For example, the journal Nature analysed the top-100 cited papers in history, to find:
